% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project at the top
\sectionTitle{Projects}{\faWrench}
%\renewcommand{\labelitemi}{$\bullet$}

\begin{projects}

    \project
        {January 2017}
        {Conferences' atendees live tracking and analysis}
        {IBM}
        {October 2017}
        {
            \begin{itemize}
                \item In less than a month, our team built a proof of concept 
                    of a solution to the registration of attendees in technical 
                    conferences, while also providing mobile applications and 
                    an RFID tracking system used to identify the attendees' 
                    participation and movement around the event's venue.
                \item Used the captured data to gain insights and create a 
                    dashboard using the Watson Analytics platform.
                \item Created several reports and graphs by cleaning and 
                    processing the raw data using Pandas and plotting with 
                    Matplotlib.
                \item A fully-working demo was tested and presented to IBM 
                    global leadership during the Interconnect conference in Las 
                    Vegas.
                \item The system was again implemented during several 
                    week-long training sessions in WeWork in Philadelphia.
            \end{itemize}
        }
        {
            Watson Analytics,
            Python,
            Pandas,
            Matplotlib,
            MySQL,
            ETL,
            RFID, 
            Linux,
            CSV,
            SQLite
        }

    \emptySeparator

    \project
        {June 2016}
        {Cognitive Concierge}
        {IBM}
        {October 2016}
        {
            \begin{itemize}
                \item By using IBM's Watson, our team trained and configured 
                    speech recognition patterns along with questions and 
                    answers in order to program a set of humanoid robots who 
                    could understand and answer natural language questions 
                    about the conference.
                \item A fully-working demo was tested and presented to the 
                    general public during the World of Watson conference in Las 
                    Vegas.
            \end{itemize}
        }
        {
            SoftBank Robotics' Nao and Pepper humanoid robots,
            Watson,
            Natural-language processing,
            Speech recognition,
            Text-to-speech,
            Speech-to-text,
            Linux,
            MySQL,
            Bluemix
        }

    \emptySeparator

    \project
        {January 2016}
        {Hadoop Raspberry Pi Cluster}
        {IBM}
        {March 2016}
        {
            \begin{itemize}
                \item I researched, analyzed and built a prototype to 
                    demonstrate the feasibility of using Raspberries as an 
                    affordable cloud offering to entry-level clients.
                \item I built a fully-working 12-node Hadoop cluster with 
                    Raspberry Pies including setting up the environment in each 
                    node, testing it and providing a demo to high management.
                \item Documented the entire process and, for benefit of the 
                    community, wrote a tutorial on how to accomplish what was 
                    done. Said guide was published on the 
                    \href{https://developer.ibm.com/recipes/tutorials/building-a-hadoop-cluster-with-raspberry-pi/}
                    {developerWorks site}.
            \end{itemize}
        }
        {
            Hadoop,
            HDFS,
            Raspbian,
            Raspberry Pi,
            SSH
        }

    \emptySeparator

    \project
        {August 2016}
        {Travel searcher}
        {Independent}
        {April 2018}
        {
            \begin{itemize}
                \item By gathering and analyzing Google's travel data, I built 
                    a wrapper and notification system to inform me of 
                    affordable flights for destinations, prices and schedules I 
                    decided.
                \item Published all the code and documentation in 
                    \href{https://github.com/alanverdugo/QPX}{my github 
                    repository}.
            \end{itemize}
        }
        {
            Python,
            Google QPX API,
            Linux,
            Cron,
            Git
        }

\end{projects}
