% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Scholarships and additional info
\sectionTitle{Education}{\faMortarBoard}

\begin{scholarship}
    \scholarshipentry{Bachelors}
        {Software engineering - Universidad Autonoma de Chihuahua}
        {
            \begin{itemize}
                \item As a final project, built a \href{https://play.google.com/store/apps/details?id=net.kippel.gilbert}{\underline{mobile application}}
                    with the goal of helping college students to learn about electricity
                    and magnetism. \href{https://github.com/alanverdugo/gilbert}{\underline{Published}}
                    the entire application as free and open source software.
                \item GPA: 3.3 - Worked full time in the tech industry in order to pay for college.
            \end{itemize}
        }
    \scholarshipentry{Associates}
        {Information technologies - Universidad Tecnologica de Chihuahua}
        {
            \begin{itemize}
                \item Besides graduating at the top of the class, completed the Cisco CCNA coursework as an extra subject.
                \item GPA: 4.0.
            \end{itemize}
        }
    \scholarshipentry{Highschool}
        {Computer technician - Technical and industrial highschool centre}
        {
            \begin{itemize}
                \item Graduated as a computer technician, focused on software development.
                \item As a class project, built a website for a local hardware store. Delivered the project to the owners in a timely manner, free of charge.
                \item Founding member of the chess club.
            \end{itemize}
        }
\end{scholarship}