% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: References
\sectionTitle{References}{\faCommentsO}

\begin{referees}
    \referee
        {Hector Avena}
        {Developer}
        {Lingo Network}
        {Alan is one of the most creative persons I know. His pragmatic and out 
        of the box thinking gives him always the advantage in any issue he 
        faces. He is a person to keep around and to brainstorm ideas with. \\
        Alan also stands out by raising the bar of the people around him, 
        either by sharing his knowledge, promoting the generation of more 
        knowledge or sharing new technologies that could help get a lead in the 
        business; IT as an ever changing business, Alan moves with the flow and 
        adapts, because of this I recommend him.}
    \referee
        {Bill Newsom}
        {Chief System Specialist}
        {AutoZone}
        {Alan is a very smart and capable programmer. He demonstrated 
        consistently a real interest is providing complete and high quality 
        service to our customers.}
    \referee
        {Anaid Chacón}
        {Product Manager}
        {Dropbox}
        {Alan is a creative and goal-oriented developer, who is never shy to 
        jump on to new challenges and learn new technologies. His attention to 
        detail and commitment towards a job well done makes him an asset to an 
        IT team. I would strongly recommend Alan for positions that require 
        analytical skills and problem solving.}
    \referee
        {Karlo Ochoa}
        {IT Technical Supervisor}
        {AutoZone}
        {Alan is a very talented and sharp person, during the time I had the 
        opportunity to work with him, he always demonstrated very good 
        programming and analytical skills, he was exposed to different systems 
        in different languages and platforms and he always showed good attitude 
        and willingness to learn and support them.\\Alan is the kind of 
        developer that always understands customer’s needs and solves their 
        problems; he is also not afraid to ask questions about the tasks he is 
        working on and always open to new challenges. I have no doubt Alan is 
        very capable and will always excels in any activity he is focus on.}
    \referee
        {Carlos Rivas}
        {Senior Programmer}
        {Clover Wireless}
        {I can recommend Alan Verdugo as a person with great recognition and 
        deep education in different programming languages and OS. Alan Verdugo 
        is a responsible and ambitious programmer. While he can be a very 
        reserved person, he shows all the time a strong determination to 
        fulfill his goals.}
    \referee
        {Luis Galindo}
        {IT Manager}
        {AutoZone}
        {Alan is a talented, focused and goal-oriented developer. His attention 
        to details and deep knowledge of his areas of expertise make Alan a key 
        member of any team he works with. Alan is always willing to take on new 
        challenges. Having Alan in the team will surely make a difference under 
        difficult situations.}
    \referee
        {Martha Culvahouse}
        {Policy and compliance manager}
        {AutoZone}
        {Alan is not only an excellent programmer but he's also a quick study 
        and extremely motivated resolution-oriented troubleshooter. An example: 
        after finishing his internship, he was assigned to support our 
        application. He took the initiative to develop serious expertise on it 
        including its peripherals and developed a wiki to support them. Suffice 
        it to say: he knew more about the application than most of the vendor's 
        technical staff.\\He's the kind of customer-oriented go-to partner that 
        helps a team succeed. I wouldn't hesitate to recommend Alan to anyone.}
    \referee
        {Mingbo Wan}
        {Production Engineer}
        {Facebook}
        {Alan's very good IT support engineer, he works very hard and have good 
        knowledge. He's the guy you can trust.}
    \referee
        {Iván Portilla}
        {Watson solution accelerator leader}
        {IBM}
        {Alan is a top-ranked IBM solution leader for Watson cognitive 
        computing engagements. Alan is recognized for his contributions to 
        boost sales figures, territory expansion and new Watson accounts 
        development.}

\end{referees}