% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Work Experience at the top
\sectionTitle{Professional experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}

\begin{experiences}
    \experience
        {November 2018}
        {Software engineer}
        {IBM}
        {Present}
        {
            \begin{itemize}
                \item Designed, developed, tested and documented code for the 
                migration of monolithic ETL processes into a continuously 
                integrated DevSecOps pipeline based on RedHat's OpenShift.
                \item Implemented and improved coding standards' compliance, 
                including PEP8, test coverage, security assessments and code 
                complexity analysis.
                \item Designed and implemented the secrets-sharing strategy of
                all our applications with Hashicorp Vault.
                \item By implementing CI/CD tools, I incremented the development 
                team's throughput while reducing the error rates and migrating 
                from an IaaS architecture to a cloud and container-based 
                architecture.
                \item Designed and implemented our monitoring strategy of all
                our applications with the use of New Relic.
				\item Our successful code builds required full PEP-8 
                compliance, unit test coverage (> 80\%), and cyclomatic complexity 
                validations, all this while adhering to IBM's strict security 
                standards.
				\item Presented local and company-wide training sessions in 
                topics like automation, monitoring, security, containers, documentation 
                and development best practices.
                \item Member of IBM's core Python team in Mexico, designing and presenting
                courses, conferences and hackatons.
                \item Co-authored two IBM Redbooks (refer to the publications section).
            \end{itemize}
        }
        {
            Python,
            OpenShift,
            FastAPI,
            GitHub,
            Docker,
            Pandas,
            Travis CI,
            Hashicorp Vault,
            DB2,
            PostgreSQL,
            RHEL,
            Xenon,
            Bandit,
            New Relic,
            LogDNA
        }

    \emptySeparator

    \experience
        {June 2018}
        {Software engineering team lead}
        {Amdocs}
        {November 2018}
        {
            \begin{itemize}
                \item Led and mentored a development team across multiple 
                geographies.
                \item Processed, analyzed and reported 
                the data of a major telecommunications company.
            \end{itemize}
        }
        {
            Python,
            Spark,
            SQL,
            ETL,
            Cassandra,
            Qlikview
        }

    \emptySeparator

    \experience
        {June 2014}
        {Software engineer}
        {IBM}
        {June 2018}
        {
            \begin{itemize}
                \item Collected, processed, curated and reported all of the 
                    billing data for IBM's AppOps Team. By enhancing existing 
                    code and developing new programs, I automated the processes 
                    and increased the revenue of the team in thousands of 
                    dollars per month.
            \end{itemize}
        }
        {
            Python,
            SQL,
            ETL,
            GitHub,
            IBM Smart Cloud Cost Manager,
            IBM Tivoli Usage and Accounting Manager,
            DB2
        }

    \emptySeparator

    \experience
        {April 2013}
        {System administrator}
        {IBM}
        {June 2014}
        {
            \begin{itemize}
                \item Supporting, troubleshooting, installing, configuring, 
                    migrating and developing all kinds of software and servers. 
                    Specialized in the Unix platform and its variants 
                    (GNU/Linux, AIX, etc.)
            \end{itemize}
        }
        {
            RHEL,
            AIX,
            Websphere Application Server,
            Nagios
        }

    \emptySeparator

    \experience
        {September 2012}
        {System administrator}
        {Electronic Arts}
        {April 2013}
        {
            \begin{itemize}
                \item Launching, supporting, troubleshooting, and enhancing
                    thousands of servers and applications in the cloud, used 
                    for videogame traffic and data processing for millions of 
                    concurrent users.
            \end{itemize}
        }
        {
            Debian,
            Python,
            MySQL,
            Nagios
        }

    \emptySeparator

    \experience
        {November 2007}
        {Programmer analyst}
        {AutoZone}
        {September 2012}
        {
            \begin{itemize}
                \item Troubleshooting, debugging, maintaining, developing and 
                    enhancing systems in a wide variety of programming 
                    languages and operating systems in a production environment 
                    for a Fortune 500 company.
                \item Received two \textit{WITTDJR (What it takes to do the job 
                    right)} awards for delivering an excellent customer service 
                    and one \textit{Extra Miller} award for \textit{"going 
                    above and beyond the call of duty, exceeding expectations 
                    and consistently doing more than expected."}
            \end{itemize}
        }
        {
            PowerBuilder, 
            SQL, 
            C, 
            Java, 
            Perl, 
            Bash, 
            Jira, 
            MySQL, 
            Informix, 
            PostgreSQL
        }

\end{experiences}
